COG-ED Manuscript

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd
fixed some bugs

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # 
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable

@@

    data_nback$nfc[i] <- data_SV$nfc[data_SV$subject == data_nback$subject[i]]

@@

  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

  data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
  data_SV$level <- as.factor(data_SV$level)

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
  library(glmmTMB)      # from the glmmTMB package for multi level models

@@

    data_nback$nfc[i] <- data_nfc$nfc[data_nfc$subject == data_nback$subject[i]]

@@

  h2b_data <- droplevels(subset(h2b_data[ ,c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

  data_SV <- unique(pipelines_data[["AARO"]][ ,c("subject","level","sv")])
